The pollination trade-off

### 2019-03-17 paper/supp-info.Rmd
Double escape math symbols in figure captions. Otherwise drake has trouble analysing dependencies
Remove unevaluated chunks from supp. info

```{r fig-deposition-log-transformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown).", eval=F}
drake::loadd(fig_pollen_density)

leg <- cowplot::get_legend(fig_pollen_density[[1]])
cowplot::plot_grid(
  remove_legend(fig_pollen_density[[1]]),
  remove_legend(fig_pollen_density[[2]]), 
  labels = LETTERS[1:2], 
  label_size = 8) %>%
  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
```

```{r fig-deposition-gain-log-transformed-or-not, fig.height = 1.8, fig.cap = "Distribution of the stigmatic pollen density for one of the bootstrap replicates used in the model sets. When (A) using directly the gain in pollen density and (B) when pollen density is log transormed (for the relative amount of conspecific pollen, density was log-transformed prior to calculating the gain).", eval=F}
drake::loadd(fig_pollen_density_diff)

leg <- cowplot::get_legend(fig_pollen_density_diff[[1]])
cowplot::plot_grid(
  remove_legend(fig_pollen_density_diff[[1]]), 
  remove_legend(fig_pollen_density_diff[[2]]), 
  labels = LETTERS[1:2], 
  label_size = 8,
  ncol = 2) %>%
  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
```

```{r fig-abundance-logtransformed-or-not, fig.height = 1.65, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one.", eval = F}
drake::loadd(fig_abundance)

cowplot::plot_grid(
  fig_abundance[[2]], 
  fig_abundance[[1]],
  rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
```

@@

```{r fig-model-results, fig.height = 5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared polinators, *p* for the visit effectiveness, and *t* for trait originality. Only candidate formulas with a $\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown. Models candidates are arranged in decreassing order of support.", eval=T}
drake::readd(fig_all_model_results)
```

```{r table-species-gain-site, results = 'asis', eval=F}
drake::loadd(significant_gain_global, significant_gain_site, sites)
table_frame <- glance_table(significant_gain_site) %>%
 dplyr::inner_join(sites, by = "site_name") %>%
  dplyr::group_by(recipient) %>%
  dplyr::mutate(n_sites = dplyr::n_distinct(site_name)) %>%
  dplyr::filter(n_sites > 1) %>%
  dplyr::group_by() %>%
  dplyr::mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  dplyr::select(recipient, site_name, estimate, statistic, p.value) %>%
  dplyr::rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient, 
         `community` = site_name)

seps <-dplyr::if_else(table_frame$`plant species` == 
  dplyr::lag(table_frame$`plant species`), "", "\\addlinespace") %>%
  na.omit()

table_frame %>%
  knitr::kable("latex", 
    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the community level. Only species present in more than one community are shown.", 
    escape = FALSE, 
    booktabs = TRUE, 
    linesep = seps, 
    digits = 3) %>%
  kableExtra::kable_styling(font_size = 8)
```

```{r table-variation-across-sites, eval=FALSE, results='asis', eval=F}
drake::loadd(consp_self)
consp_self %>%
  anova(test = "Chisq")  %>%
  knitr::kable("latex", 
    caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.',
    booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8)
```

@@

```{r fig_effect_quant_qual, fig.height=3.5, fig.cap="asd", eval=F}
drake::loadd(fig_effect_quant_qual)

cowplot::plot_grid(
 fig_effect_quant_qual[[1]], 
 fig_effect_quant_qual[[2]],
  labels = LETTERS[1:2], 
  label_size = 8, ncol = 2)
```

>>>>

@@

```{r fig-model-results, fig.height = 5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared polinators, *p* for the visit effectiveness, and *t* for trait originality. Only candidate formulas with a $\\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown. Models candidates are arranged in decreassing order of support.", eval=T}
drake::readd(fig_all_model_results)
```

@@
